Library-based fault tolerance for scientific applications

### 2013-01-07 report.tex
Makefile and tex file for pdflatex

% The following \documentclass options may be useful:
%
% 10pt          To set in 10-point type instead of 9-point.
% 11pt          To set in 11-point type instead of 9-point.
% authoryear    To obtain author/year citation style instead of numeric.
\usepackage{fontspec}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{color}
\usepackage{multirow}
\usepackage{sectsty}
\usepackage[titles]{tocloft}
\usepackage{sidecap}
\usepackage{multicol}

@@

\begin{SCfigure}
\includegraphics[width=6cm]{routine_markov.png}
\caption{The Markov Model illustrating a numerical routine we're interested in. This routine, under the effects of soft errors, may abort and produce no results at all or it produce erroneous results or under some circumstances produce correct results. If the user keeps restart the application in case of error, the expected completion time of the routine could be computed as $T=(2-c)B+{{1-c} \over {c}} \cdot R$}
\label{markovModel}
\end{SCfigure}

@@

\begin{SCfigure}
\includegraphics[width=6cm]{vuln-gsl.png}
\caption{Error vulnerability of GSL routines. The figure shows the fraction of entries in the output matrix (the vertical axis) that have an error large than some magnitude (the horizontal axis). The fault-tolerance mechanism we have used here have reduced the occurances of errors of all magnitudes by one magnitude for routines Rank-K update and Matrix-matrix multication, and has removed the worst errors in the TRSV linear solver. This proves the fault-tolerant versions of the routines are effective.}
\label{vulnerabilityGSL}
\end{SCfigure}

@@

\begin{SCfigure}
\includegraphics[width=8cm]{flow.png}
\caption{Block diagram of fault-tolerant routines showing various parts: input backup, the original routine, result checkers and input restoration. The entire fault-tolerant routine is wrapped in a function call that has the same argument format as the original one, making it easy to be seamlessly integrated into applications.}
\label{faultRoutinesBlockDiagram}
\end{SCfigure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=10cm]{n_replica_correct_runs_cdb1.png}
\end{center}
\caption{Effectiveness of pointer and index replication in RK4 integrator. The X axis is how many times each pair of replica is used and the Y axis is how many occurrances of a loop variable to protect. Obviously, we have the best resilience when all occurrances are protected. The interesting discovery is that using each replica twice instead of once has the best resilience. The color of the cells indicate the relative resilience: the brighter, the more resilient.}
\label{fig:greenMtx}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=16cm]{OverallMetric_Lasso_Boxplot.png}
\end{center}
\caption{Visualization of overall metrics of 73718 runs of Lasso throuout 256 different configurations. The facets correspond to different input sizes. The X and Y axes inside one facet correspond to different error checker thresholds and the overall metrics.}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=16cm]{Overall_Metric_DRC.png}
\end{center}
\caption{Visualization of overall metrics of 14936 runs of DRC throughout 95 different configurations. The facets correspond to different input sizes. The X and Y axes inside one facet correspond to different error checker thresholds and the overall metrics.}
\end{figure}

@@

\begin{SCfigure}
\includegraphics[width=8cm]{model1.png}
\label{markovModel}
\caption{Markov Model used for modeling running time under low error rates.}
\end{SCfigure}

>>>>

% The following \documentclass options may be useful:
%
% 10pt          To set in 10-point type instead of 9-point.
% 11pt          To set in 11-point type instead of 9-point.
% authoryear    To obtain author/year citation style instead of numeric.
%\usepackage{fontspec} % Doesn't work with LaTeX
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{color}
%\usepackage{multirow}
%\usepackage{sectsty}
%\usepackage[titles]{tocloft}
%\usepackage{sidecap}
\usepackage{multicol}

@@

\begin{figure}
\includegraphics[width=6cm,natwidth=398,natheight=162]{routine_markov.png}
\caption{The Markov Model illustrating a numerical routine we're interested in. This routine, under the effects of soft errors, may abort and produce no results at all or it produce erroneous results or under some circumstances produce correct results. If the user keeps restart the application in case of error, the expected completion time of the routine could be computed as $T=(2-c)B+{{1-c} \over {c}} \cdot R$}
\label{markovModel}
\end{figure}

@@

\begin{figure}
\includegraphics[width=6cm,natwidth=440,natheight=401]{vuln-gsl.png}
\caption{Error vulnerability of GSL routines. The figure shows the fraction of entries in the output matrix (the vertical axis) that have an error large than some magnitude (the horizontal axis). The fault-tolerance mechanism we have used here have reduced the occurances of errors of all magnitudes by one magnitude for routines Rank-K update and Matrix-matrix multication, and has removed the worst errors in the TRSV linear solver. This proves the fault-tolerant versions of the routines are effective.}
\label{vulnerabilityGSL}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8cm,natwidth=560,natheight=507]{flow.png}
\caption{Block diagram of fault-tolerant routines showing various parts: input backup, the original routine, result checkers and input restoration. The entire fault-tolerant routine is wrapped in a function call that has the same argument format as the original one, making it easy to be seamlessly integrated into applications.}
\label{faultRoutinesBlockDiagram}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=10cm,natwidth=1000,natheight=800]{n_replica_correct_runs_cdb1.png}
\end{center}
\caption{Effectiveness of pointer and index replication in RK4 integrator. The X axis is how many times each pair of replica is used and the Y axis is how many occurrances of a loop variable to protect. Obviously, we have the best resilience when all occurrances are protected. The interesting discovery is that using each replica twice instead of once has the best resilience. The color of the cells indicate the relative resilience: the brighter, the more resilient.}
\label{fig:greenMtx}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=16cm,natwidth=1156,natheight=725]{OverallMetric_Lasso_Boxplot.png}
\end{center}
\caption{Visualization of overall metrics of 73718 runs of Lasso throuout 256 different configurations. The facets correspond to different input sizes. The X and Y axes inside one facet correspond to different error checker thresholds and the overall metrics.}
\end{figure}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=16cm,natwidth=1160,natheight=744]{Overall_Metric_DRC.png}
\end{center}
\caption{Visualization of overall metrics of 14936 runs of DRC throughout 95 different configurations. The facets correspond to different input sizes. The X and Y axes inside one facet correspond to different error checker thresholds and the overall metrics.}
\end{figure}

@@

\begin{figure}
\includegraphics[width=8cm,natwidth=488,natheight=243]{model1.png}
\label{markovModel}
\caption{Markov Model used for modeling running time under low error rates.}
\end{figure}
